### 2024-10-10 manuscript.tex
[ref]: Update Sutanu's citation in the text [ci skip]
This build is based on
https://github.com/pivlab/annual_review_of_biomedical_data_science/commit/8a837d579f9d6b75e3a316e920ed7a60d14fcfc5.

This commit was created by the following CI build and job:
https://github.com/pivlab/annual_review_of_biomedical_data_science/commit/8a837d579f9d6b75e3a316e920ed7a60d14fcfc5/checks
https://github.com/pivlab/annual_review_of_biomedical_data_science/actions/runs/11282703200

This manuscript
(\href{https://pivlab.github.io/annual_review_of_biomedical_data_science/v/876267bf5f5cb653b6898a4b032be3be7ca3b9f8/}{permalink})
was automatically generated
from \href{https://github.com/pivlab/annual_review_of_biomedical_data_science/tree/876267bf5f5cb653b6898a4b032be3be7ca3b9f8}{pivlab/annual\_review\_of\_biomedical\_data\_science@876267b}
on October 10, 2024.

@@

Understanding the genetic basis of complex traits is a longstanding challenge in the field of genomics.
Genome-wide association studies (GWAS) have identified thousands of variant-trait associations, but most of these variants are located in non-coding regions, making the link to biological function elusive.
While traditional approaches, such as Transcriptome-wide association studies (TWAS), have advanced our understanding by linking genetic variants to gene expression, they often overlook gene-gene interactions.
Here, we review current approaches based on gene modules to integrate different molecular data, leveraging machine learning methods to identify gene modules based on co-expression and functional relationships.
These integrative approaches, like PhenoPLIER, combine TWAS and drug-induced transcriptional profiles to effectively capture biologically meaningful gene networks.
This integration provides a context-specific understanding of disease proceses while highlighting both core and peripheral genes.
These insights pave the way for novel therapeutic targets and enhance the interpretability of genetic studies in personalized medicine.

@@

\leavevmode\vadjust pre{\hypertarget{ref-xJjWGVyN}{}}%
\CSLLeftMargin{87. }%
\CSLRightInline{\textbf{GWAS Catalog} \url{https://www.ebi.ac.uk/gwas/genes/DGAT2}}

>>>>

This manuscript
(\href{https://pivlab.github.io/annual_review_of_biomedical_data_science/v/8a837d579f9d6b75e3a316e920ed7a60d14fcfc5/}{permalink})
was automatically generated
from \href{https://github.com/pivlab/annual_review_of_biomedical_data_science/tree/8a837d579f9d6b75e3a316e920ed7a60d14fcfc5}{pivlab/annual\_review\_of\_biomedical\_data\_science@8a837d5}
on October 10, 2024.

@@

This is a very cool paper about something.
We are doing this and that.
And this are the conclusions.
And this is in \textbf{boldface}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-xJjWGVyN}{}}%
\CSLLeftMargin{87. }%
\CSLRightInline{\url{https://www.ebi.ac.uk/gwas/genes/DGAT2}}
